\vspace{-0.25em}\thetitle

### 2009-07-17 paper.tex
...

Our key observation is that real-world network traces tend to have approximately low-rank representation matrices despite the potential rank of such matrices being very large.
Moreover, most flows' vectors lie on only one of a few even lower rank subspaces.
Real traffic lies near the union of a small set of very low rank subspaces in the huge potential space of representations.
Moreover, the low-rank subspace near which real traffic lies can be decomposed into subspaces of even lower rank, with almost all flows lying in one of these subspaces.
Typically, these smaller subspaces are one-dimensional, but in some cases they may have up to a dozen dimensions.

>>>>

The essential observation of this research is that real traffic lies near the union of a small set of low rank subspaces in the representation space.
This allows us to perform a drastic model reduction on traffic data while preserving most characteristics of the original traffic.
Moreover, when observable characteristics of flows are separated from features to be predicted, this model reduction is similar to a classical linear regression, and allows us to very simply predict unseen behavior of flows.
We apply this technique here to directly predict the following characteristics of each flow from observing only a handful of its initial packets:
\begin{enumerate}
  \item the distribution of packets sizes,
  \item the distribution of inter-packet intervals,
  \item the number of packets that will be in the flow.
\end{enumerate}
From these properties, we can indirectly predict many other properties, including the total duration and data volume.
% 
% real-world network traces tend to have approximately low-rank representation matrices despite the potential rank of such matrices being very large.
% Moreover, most flows' vectors lie on only one of a few even lower rank subspaces.
% Moreover, the low-rank subspace near which real traffic lies can be decomposed into subspaces of even lower rank, with almost all flows lying in one of these subspaces.
% Typically, these smaller subspaces are one-dimensional, but in some cases they may have up to a dozen dimensions.
